Inferring probabilistic stellar rotation periods using Gaussian processes

### 2017-07-07 documents/ms.tex
removing figures path

\begin{figure*}
\begin{center}
% \includegraphics[width=6in, clip=true]{compare_mcmc.pdf}
\includegraphics[width=6in, clip=true]{figures/comparison_acfprior_03_10.pdf}
\caption{The `true' rotation periods used to generate \naigrain\
simulated light curves vs the rotation periods measured using the GP
technique with an informed, ACF-based prior.
    Points are coloured by the peak-to-peak amplitude of the light curve, as
    defined in \citet{Aigrain2015}.
Since the posterior PDFs of rotation periods are often non-Gaussian,
    the points plotted here are maximum {\it a-posteriori} results.
The uncertainties are the 16th and 84th percentiles.
In many cases, the uncertainties are under-estimated.
The ACF-informed prior on rotation period used to generate these results is
    described in \textsection \ref{sec:GP_prior}.
    }
\label{fig:compare_mcmc_acfprior}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=6in, clip=true]{figures/comparison_noprior_02_13.pdf}
\caption{The `true' rotation periods used to generate \naigrain\
simulated light curves vs the rotation periods measured using the GP
technique with an uninformative prior.
    Points are coloured by the peak-to-peak amplitude of the light curve, as
    defined in \citet{Aigrain2015}.
Since the posterior PDFs of rotation periods are often non-Gaussian,
    the points plotted here are maximum {\it a-posteriori} results.
The uncertainties are the 16th and 84th percentiles.
In many cases, the uncertainties are under-estimated.
An uninformative prior, flat in the natural log of the rotation period between
    0.5 and 100 days was used to generate these results.
    }
\label{fig:compare_mcmc_noprior}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=6in, clip=true]{figures/corner_plot.pdf}
\caption{Marginal posterior PDFs of the QP GP model parameters, fit to the
    simulated light curve in figure \ref{fig:demo_lc}.
    The blue line in the period panel shows the injected period.
    This figure was made using \texttt{corner.py} \citep{Corner}.}
\label{fig:gp_posteriors}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
% \includegraphics[width=6in, clip=true]{compare_pgram.pdf}
\includegraphics[width=6in, clip=true]{figures/compare_pgram_filtered_35.pdf}
\caption[LS periodogram results.]
{The `true' rotation periods used to generate \naigrain\ simulated light
curves vs the rotation periods measured using a LS periodogram technique.
    Points are coloured by the peak-to-peak amplitude of the light curve, as
    defined in \citet{Aigrain2015}.
In many cases a large peak at a long period was present in the periodogram,
    producing a significant over-estimate of the period.
    }
\label{fig:pgram_compare}
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
% \includegraphics[width=6in, clip=true]{compare_mcmc.pdf}
\includegraphics[width=6in, clip=true]{comparison_acfprior_03_10.pdf}
\caption{The `true' rotation periods used to generate \naigrain\
simulated light curves vs the rotation periods measured using the GP
technique with an informed, ACF-based prior.
    Points are coloured by the peak-to-peak amplitude of the light curve, as
    defined in \citet{Aigrain2015}.
Since the posterior PDFs of rotation periods are often non-Gaussian,
    the points plotted here are maximum {\it a-posteriori} results.
The uncertainties are the 16th and 84th percentiles.
In many cases, the uncertainties are under-estimated.
The ACF-informed prior on rotation period used to generate these results is
    described in \textsection \ref{sec:GP_prior}.
    }
\label{fig:compare_mcmc_acfprior}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=6in, clip=true]{comparison_noprior_02_13.pdf}
\caption{The `true' rotation periods used to generate \naigrain\
simulated light curves vs the rotation periods measured using the GP
technique with an uninformative prior.
    Points are coloured by the peak-to-peak amplitude of the light curve, as
    defined in \citet{Aigrain2015}.
Since the posterior PDFs of rotation periods are often non-Gaussian,
    the points plotted here are maximum {\it a-posteriori} results.
The uncertainties are the 16th and 84th percentiles.
In many cases, the uncertainties are under-estimated.
An uninformative prior, flat in the natural log of the rotation period between
    0.5 and 100 days was used to generate these results.
    }
\label{fig:compare_mcmc_noprior}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=6in, clip=true]{corner_plot.pdf}
\caption{Marginal posterior PDFs of the QP GP model parameters, fit to the
    simulated light curve in figure \ref{fig:demo_lc}.
    The blue line in the period panel shows the injected period.
    This figure was made using \texttt{corner.py} \citep{Corner}.}
\label{fig:gp_posteriors}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
% \includegraphics[width=6in, clip=true]{compare_pgram.pdf}
\includegraphics[width=6in, clip=true]{compare_pgram_filtered_35.pdf}
\caption[LS periodogram results.]
{The `true' rotation periods used to generate \naigrain\ simulated light
curves vs the rotation periods measured using a LS periodogram technique.
    Points are coloured by the peak-to-peak amplitude of the light curve, as
    defined in \citet{Aigrain2015}.
In many cases a large peak at a long period was present in the periodogram,
    producing a significant over-estimate of the period.
    }
\label{fig:pgram_compare}
\end{center}
\end{figure*}
